% the acknowledgments section

Here's to my own influences!

First of all, I would like to thank my advisers, Yaron Singer and Mark Glickman for putting up with me taking on this passion project for my senior thesis. Besides being brilliant people, you are also two of the most genuine human beings I have met during my time at Harvard. In all likelihood, in 20 years all three of us probably will have forgotten about this thesis, but I will never forget your kindness towards me.

I thank James Waldo for graciously agreeing to being a reader for this thesis.

I thank Raghu Dhara, Mark Goldstein and Kojin Oshiba for their invaluable advice in helping me brainstorm ideas for this thesis.

I would like to thank my suitemates: Chris Chen, Josh Felizardo, Phillip Huang and Mario Menendez. True friends are hard to find in this world; hopefully this means that you'll still talk to me after graduation.

I thank Dan Fox, Jeff Harrington, Mark Kaplan, Mark Olson, Paul Pitts, Peter Tileston and the many other musical mentors I have had over the years who helped instill an undying love for music in me. I've learned so much from music beyond just the notes, and it's in no small part due to you.

To Jasper Schilling, one of the few people that I will admit is perhaps a bigger music fan than me. Thanks for being a friend all these years, and I wish you the best as you embark on your own career in music.

I thank my little sister, Weian for always being adorable. Enough said.

Finally, I have to thank my parents, whom I really can't thank enough. I know that I may not always show it, but I truly love you with all my heart and am grateful for all the sacrifices you have made for me over the years. \textit{Ma}, thank you for always being a great listener and for your indefatigable love. \textit{Ba}, thank you for showing me by example how to be my own man. My time in college has not always been smooth sailing, but you two helped me see it through. Thank you. This is for you.



